Intelligent Reflecting Surface-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design

### 2021-03-10 main.tex
:wrench: Update config

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_tx}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_tx.tex}
				}
			}
			\subfloat[WIT SNR and WPT DC current\label{fi:scaling_tx}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/scaling_tx.tex}
				}
			}
			\caption{Average R-E region, WIT SNR and WPT DC current versus $M$ for $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_reflector}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_reflector.tex}
				}
			}
			\subfloat[WIT SNR and WPT DC current\label{fi:scaling_reflector}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/scaling_reflector.tex}
				}
			}
			\caption{Average R-E region, WIT SNR and WPT DC current versus $L$ for $M=1$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
		\end{figure}

>>>>

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_tx}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_tx.tex}
				}
			}
			\subfloat[WIT SNR and WPT DC current\label{fi:scaling_tx}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/scaling_tx.tex}
				}
			}
			\caption{Average R-E region, WIT SNR and WPT DC current versus $M$ for $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$, $d_{\mathrm{H}}=d_{\mathrm{V}}=0.5\,\si{\meter}$.}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_reflector}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_reflector.tex}
				}
			}
			\subfloat[WIT SNR and WPT DC current\label{fi:scaling_reflector}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/scaling_reflector.tex}
				}
			}
			\caption{Average R-E region, WIT SNR and WPT DC current versus $L$ for $M=1$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=0.5\,\si{\meter}$.}
		\end{figure}
